Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study

### 2020-08-18 paper/aimusic2020/paper.tex
Add authors, titles and minor formatting changes

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{apacite}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% first the title is needed
\title{Neural Models for Target-Based Computer-Assisted Musical Orchestration}

% a short form should be given in case it is too long for the running head
\titlerunning{Running Title}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{AuthorA\inst{1}\and AuthorB\inst{2} \thanks{Please place acknowledgement here.}}
%
% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
\authorrunning{AuthorA and AuthorB (or AuthorA et al. if too long)}

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{InstituteA \and InstituteB\\ \email{author@phdsrus.ac.uk}}

@@

\begin{figure}
\includegraphics[scale=0.17]{../latex/figs/method.png}
\caption{An overview of the proposed method for assisted orchestration with neural models. Instruments and pitches are determined as peaks of the output probability distribution, while the dynamics are computed by quantizing the probabilities. \label{fig:method}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.22]{../latex/figs/CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{center}
\end{figure}

@@

%\begin{table}
%\begin{center}
%\begin{tabular}{|c|c|c|}
%\hline
%\textbf{Instrument} & \textbf{Abbreviation} & \textbf{Range} \\
%\hline
%Violin & Vn & G3-E7\\
%Cello & Vc & C2-C6\\
%Viola & Va & C3-C7\\
%Trumpet C & TpC & F\#3-C6\\
%Trombone & Tbn & A\#0;A\#1-C5\\
%Oboe & Ob & A\#3-A6\\
%Horn & Hn & G1-F5\\
%Flute & Fl & B3-D7\\
%Clarinet Bb & ClBb & D3-G6\\
%Contrabass & Cb & E1-C5\\
%Bass Tuba & BTb & F\#1-F4\\
%Bassoon & Bn & A\#1-D\#5\\
%\hline
%\end{tabular}
%\caption{Table showing the pitch ranges present in the TinySOL database.\label{tab:ranges}}
%\end{center}
%\end{table}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|c|c|c|c|} 
    	  \hline
      \textbf{Instr. 1} & \textbf{Instr. 2} & \textbf{SVM Acc.} & \textbf{RF Acc.}\\
      \hline
      Violin & Flute & 38.8\% & 9.8\% \\
      \hline
      Violin & Trumpet & 33.8\% & 9.1\% \\
      \hline
      Violin & Cello & 34.8\% & 6.3\% \\
      \hline
      Cello & Viola & 32.1\% & 5.8\% \\
      \hline
      Oboe & French Horn & \textbf{39.9\%} & \textbf{17.5\%} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Comparison of accuracies between SVM and RF. Each data point is a combination of two TinySOL samples, where at least one of the samples is from one of the two instruments specified for that experiment. For the samples drawn from one of the two instruments, the pitch class of that sample is identified. For a sample not from one of the two instruments, the classifier simply attempted to identify that a sample from one of the non-specified instruments was present. In this setting, there are 25 classes: 24 from the 12 pitch classes from 2 instruments, and 1 class that specified whether an instrument that is not one of the two specified is present. \label{tab:baselines}}
\end{table}

@@

\begin{table*}
  \begin{center}
    \label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \ref{distance} was used with $\lambda_1 = 0.5$ and $\lambda_2 = 10$ to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}
\end{table*}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{url}
\usepackage{apacite}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% first the title is needed
\title{Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study}

% a short form should be given in case it is too long for the running head
\titlerunning{Neural Models for Target-Based Computer-Assisted Musical Orchestration}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Carmine Emanuele Cella\inst{1}\and Luke Dzwonczyk\inst{1}\and Alejandro Saldarriaga-Fuertes\inst{1}\and Hongfu Liu\inst{2}\and Helene-Camille Crayencour\inst{3} \thanks{Please place acknowledgement here.}}
%
% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
\authorrunning{Carmine Emanuele Cella et al.}

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Unviersity of California, Berkeley \and InstituteB\\ \email{author@phdsrus.ac.uk}}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.17]{../latex/figs/method.png}
	\caption{An overview of the proposed method for assisted orchestration with neural models. Instruments and pitches are determined as peaks of the output probability distribution, while the dynamics are computed by quantizing the probabilities. \label{fig:method}}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.22]{../latex/figs/CNN_LSTM_diagram.png}
	\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure}

@@

@@

\begin{table}
  \centering
  \caption{Comparison of accuracies between SVM and RF. Each data point is a combination of two TinySOL samples, where at least one of the samples is from one of the two instruments specified for that experiment. For the samples drawn from one of the two instruments, the pitch class of that sample is identified. For a sample not from one of the two instruments, the classifier simply attempted to identify that a sample from one of the non-specified instruments was present. In this setting, there are 25 classes: 24 from the 12 pitch classes from 2 instruments, and 1 class that specified whether an instrument that is not one of the two specified is present. \label{tab:baselines}}
    \begin{tabular}{|c|c|c|c|} 
    	  \hline
      \textbf{Instr. 1} & \textbf{Instr. 2} & \textbf{SVM Acc.} & \textbf{RF Acc.}\\
      \hline
      Violin & Flute & 38.8\% & 9.8\% \\
      \hline
      Violin & Trumpet & 33.8\% & 9.1\% \\
      \hline
      Violin & Cello & 34.8\% & 6.3\% \\
      \hline
      Cello & Viola & 32.1\% & 5.8\% \\
      \hline
      Oboe & French Horn & \textbf{39.9\%} & \textbf{17.5\%} \\
      \hline
    \end{tabular}
\end{table}

@@

\begin{table*}
  \centering
     \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \ref{distance} was used with $\lambda_1 = 0.5$ and $\lambda_2 = 10$ to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}\label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}

\end{table*}
